### 2020-02-01 thesis/paper.tex
more sections

\section{Class Interfaces and Implementations}
To ensure that new or missing methods can easily be added to the tool, all methods where a selection can be made from within the tool can be added to by implementing onto the corresponding interface. To add methods one needs to first implement it and if needed it's OptionsPanel and then add it to the corresponding static method found in the view using it.

>>>>

\section{File Input and Output}
\subsection{Clustering Data}

\subsection{Clustering Workflows}

\subsection{Pre-Clustered Data}

\section{Methods and Interfaces}
To ensure that new or missing methods can easily be added to the tool, all methods where a selection can be made from within the tool can be added to by implementing onto the corresponding interface. To add methods one needs to first implement it and if needed it's OptionsPanel and then add it to the corresponding static method found in the view using it.
